Scikit-learn: machine learning without learning the machinery

### 2014-05-21 article.tex
Compress code example

@@

@@

% XXX make_pipeline is not in 0.14.1, we should release 0.15 sometime
% The example can be made a bit shorter by skipping the movie_reviews dir;
% the tarball from Pang et al. contain top-level cruft.
\begin{lstlisting}
import os.path
import tarfile
from urllib import urlretrieve
from sklearn.datasets import load_files
from sklearn.feature_extraction.text import TfidfVectorizer
from sklearn.linear_models import LogisticRegression
from sklearn.pipeline import make_pipeline

temp, _ = urlretrieve('http://preview.tinyurl.com/review-tgz')
with tarfile.open(temp) as tar:
    tar.extractall(path='movie_reviews')
data = load_files(os.path.join('movie_reviews', 'txt_sentoken'))

clf = make_pipeline(TfidfVectorizer(min_df=2, dtype=float,
                                    sublinear_tf=True, ngram_range=(1, 2),
                                    strip_accents='unicode'),
                     LogisticRegression(random_state=623, C=5000))
clf.fit(data.data, data.target)
\end{lstlisting}

>>>>

% Listing settings for Python
\lstset{language=python,
	extendedchars=true,
	xleftmargin = 0pt,
	%frame=single,
	%rulecolor=\color{lightgrey},
        aboveskip = 0.5ex,
        belowskip = 0.6ex,
	basicstyle=\small\sffamily,
	escapebegin={\color{green}},
        keywordstyle=\bfseries\color{blue!50!black},
	%identifierstyle=\sffamily\small,
	commentstyle=\color{green!40!black},
	stringstyle=\rmfamily\color{red!60!black},
	showstringspaces=false,
	tabsize=2,
	breaklines=true,
	%classoffset=1,
        morekeywords={{,},=,:}, %keywordstyle=\color{SkoleYellow},
	%classoffset=0,
	backgroundcolor=\color{green!10},
	fillcolor=\color{green!10},
}

@@

\begin{figure*}
\lstinputlisting[lastline=12]{nlp_example.py}
\end{figure*}

@@

% XXX make_pipeline is not in 0.14.1, we should release 0.15 sometime
% The example can be made a bit shorter by skipping the movie_reviews dir;
% the tarball from Pang et al. contain top-level cruft.
%\begin{lstlisting}
%import os.path
%import tarfile
%from urllib import urlretrieve
%from sklearn.datasets import load_files
%from sklearn.feature_extraction.text import TfidfVectorizer
%from sklearn.linear_models import LogisticRegression
%from sklearn.pipeline import make_pipeline
%
%temp, _ = urlretrieve('http://preview.tinyurl.com/review-tgz')
%with tarfile.open(temp) as tar:
%    tar.extractall(path='movie_reviews')
%data = load_files(os.path.join('movie_reviews', 'txt_sentoken'))
%
%clf = make_pipeline(TfidfVectorizer(min_df=2, dtype=float,
%                                    sublinear_tf=True, ngram_range=(1, 2),
%                                    strip_accents='unicode'),
%                     LogisticRegression(random_state=623, C=5000))
%clf.fit(data.data, data.target)
%\end{lstlisting}
